Age-related changes in plant growth and traits

### 2015-05-19 results_growth.Rmd
bit of work on growth file

source("scripts/summary_dataframes.R")
```
#Growth data, general patterns
- proportion of maxH matters more for some species than others. 
  1. The 4 "canopy" species all tend to have high correlations between "prop maxH" and growth and reproductive investment (both relative and absolute)  
  2. The lower-growing species are more variable, with "prop maxH mattering more for some than others"

@@

Generic functions for most plotting below
```{r, echo=FALSE, message=FALSE}
plot_yvar_vs_xvar <- function(data, yvar = "y", xvar = "x", ...) {
  Y <- data[[yvar]]
  X <- data[[xvar]]
  plot(Y ~ X, data=data,  cex.axis=.8, las=1, pch=16, ...)
}

summarise_fit <- function(x) {
  data.frame(
    select(glance(x), r.squared, p.value),
    n= length(resid(x)),
    a = coef(x)[1],
    b = coef(x)[2]
  )
}

summarise_all_fits <- function(x) {
  tmp <- lapply(x, summarise_fit) %>%
    bind_rows
  data.frame(species=names(x), tmp)
}
```

@@

```{r, echo=FALSE, message=FALSE}
plot((FinalWeight~PropH), SummaryInd, col=col.spp[as.factor(species)],pch=16,log="y")
legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
plot((FinalWeight~StartBasalDiamAv), SummaryInd, col=col.spp[as.factor(species)],pch=16,log="xy")

@@

```{r, echo=FALSE, message=FALSE}
plot((GrowthInv~PropH), SummaryInd, log="y", col=col.spp[as.factor(species)],pch=16)
legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")

@@

for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar, log="y",
                    main=spp, xlab=xvar, ylab=yvar)

@@

```{r, echo=FALSE, message=FALSE}
plot((RGR~PropH), SummaryInd, col=col.spp[as.factor(species)],pch=16)
legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")

yvar <- "RGR"
xvar <- "PropH"

@@

for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,
                    main=spp, xlab=xvar, ylab=yvar)
  abline(lmfits[[spp]])
}
```

###PropH by age
- Confirming that species get taller as they get older  
- Obviously true for most species, but some (i.e. PILI, somewhat BOLE, HEPU) they reach their "maxH" within a few years and then the relationship is mostly flat. These are of course also the species which are shorter lived and have high levels of early reproduction

```{r, echo=FALSE, message=FALSE}
yvar <- "PropH"
xvar <- "age"

>>>>

source("scripts/summary_dataframes.R")
source("scripts/functions.R")
```
#Growth data, general patterns
- proportion of maxH matters more for some species than others. 
  1. The 4 "canopy" species all tend to have high correlations between "prop maxH" and growth and reproductive investment (both relative and absolute)  
  2. The lower-growing species are more variable, with "prop maxH mattering more for some than others"

@@

@@

```{r, echo=FALSE, message=FALSE}
plot((FinalWeight~PropH), SummaryInd, col=col.spp[as.factor(species)],pch=16,log="y")
legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")

@@

```{r, echo=FALSE,message=FALSE,fig.width=14, fig.height=7}
par(mfrow=c(1,2), cex=1, omi=c(.1,0.3,.5,0.2), mai=c(1.1,1,.1,0.2))
plot((GrowthInv~PropH), SummaryInd, log="y", col=col.spp[as.factor(species)],pch=16)
legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")

@@

results
```

```{r, echo=FALSE,message=FALSE, fig.width=7, fig.height=7}
par(mfrow=c(1,1), cex=1, omi=c(.1,.1,.1,.1), mai=c(1.1,1.1,.1,0.2)) 
for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar, log="y",
                    main=spp, xlab=xvar, ylab=yvar)

@@

```{r, echo=FALSE, message=FALSE}
yvar <- "RGR"
xvar <- "PropH"

@@

results
```
